### 2013-11-09 article2013.Rmd
Tein takautuvasti vielä muutokset artikkelin taulukkokoodeihin ja poistin jotain mitä olin jo poistanut. (siis olisi pitänyt committaa uusimmat muutokset ennen mikko branchin yhdistämistä)

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(knitr)
knit("article2013.Rmd")
system("~/.cabal/bin/pandoc article2013.md --number-sections -o article2013.pdf")
system("~/.cabal/bin/pandoc -s article2013.md --toc --number-sections -o article2013.html")
system("~/.cabal/bin/pandoc -f markdown -t docx article2013.md -o article2013.docx --standalone --toc --number-sections")
system("~/.cabal/bin/pandoc article2013.md -o article2013.epub --standalone --toc --number-sections")

@@

-----------------------------------------------------------------------------
Variable                    Description
------------------------    -------------------------------------------------
Individual-level

@@

Country-level

@@

```{rattribArticleDescTbl1, results='asis'}
source("code/dv_tables.R")
library(xtable)
print.xtable(xtable(tbl5, 
                    caption="Weighted population shares of dependent variable by country",),
              type="html",
              comment=FALSE, 
              include.rownames=FALSE,
             caption.placement="top")

@@

![Change in total GDP in 2007 - 2010 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_gdp.png)

@@

![Gini coefficient and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_gini.png)

@@

![World Bank's Voice and Accountability index in 2011 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_wbgi.png)

>Voice and accountability captures perceptions of the extent to which a country's citizens are able to participate in selecting their government, as well as freedom of expression, freedom of association, and a free media. [info.worldbank.org/governance/wgi/pdf/va.pdf](http://info.worldbank.org/governance/wgi/pdf/va.png)

@@

*There we some issues in converts regression outputs so the tables are evolving and can be browsed at: [http://research.muuankarski.org/attributions/code/multilevel_models.html](http://research.muuankarski.org/attributions/code/multilevel_models.html)*

****

<!--

As the main controbution of our study relates to cross-national variation of attributions for poverty within post-socialist countries, we shall largely focus on the effects of contextual variables. Nevertheless, as we are covering several countries that haven't been included in previous studies of individual level determinants, we shall also look carefully at the individual level.

-->

>>>>

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(knitr)
knit("article2013.Rmd")
system("~/.cabal/bin/pandoc article2013.md --template=../../../template/pandoc_article/tex_templates/pandoc.latex.template --number-sections --latex-engine=xelatex -o article2013.pdf")
system("~/.cabal/bin/pandoc article2013.md  --number-sections -o article2013.pdf")

system("~/.cabal/bin/pandoc -s article2013.md --toc --number-sections -o article2013.html")
system("~/.cabal/bin/pandoc -f markdown -t docx article2013.md -o article2013.docx --standalone --toc --number-sections")
system("~/.cabal/bin/pandoc article2013.md -o article2013.epub --standalone --toc --number-sections")

@@

-----------------------------------------------------------------------------
Variable                    Description
------------------------    -------------------------------------------------
**Individual-level**

@@

**Country-level**

@@

```{rattribArticleDescTbl1, results='asis'}
source("code/dv_tables.R")
library(xtable)
print.xtable(xtable(tbl5, 
                    caption="Weighted population shares of dependent variable by country",),table.placement="H",
             type="latex",
             comment=FALSE, 
             include.rownames=FALSE,
             caption.placement="top")

@@

![Change in total GDP in 2007 - 2010 and support for social (top) and individual (bottom) blame types of attributions for poverty](figure/scatter_gdp.pdf)

@@

![Gini coefficient and support for social (top) and individual (bottom) blame types of attributions for poverty](figure/scatter_gini.pdf)

@@

![World Bank's Voice and Accountability index in 2011 and support for social (top) and individual (bottom) blame types of attributions for poverty](figure/scatter_wbgi.pdf)

>Voice and accountability captures perceptions of the extent to which a country's citizens are able to participate in selecting their government, as well as freedom of expression, freedom of association, and a free media. [info.worldbank.org/governance/wgi/pdf/va.pdf](http://info.worldbank.org/governance/wgi/pdf/va.pdf)

@@

*As the main controbution of our study relates to cross-national variation of attributions for poverty within post-socialist countries, we shall largely focus on the effects of contextual variables. Nevertheless, as we are covering several countries that haven't been included in previous studies of individual level determinants, we shall also look carefully at the individual level.*

```{rarticleModels, results='asis', eval=TRUE}
load("data/finalModels.RData")

model.names.multi.2 = c("SB vs. not",
                        "IB vs. not",
                        "SB vs. IB")

coef.names.multi = c("(intercept)",
                     "Dependent","Low education",
                     "Low income","Income has worsened",
                     "Income will worsen","Has affected great or fair amount",
                     "Gini coefficient",
                     "Change in GDP between 2007 to 2010",
                     "Good governance")

library(texreg)
texreg(list(soc.4,ind.4,socVsInc),float.pos="H",
       use.packages=TRUE,
       #booktabs=TRUE,
       #dcolumn=TRUE,
       #sideways=TRUE,
       naive = TRUE,
       caption.above=TRUE,
       doctype=FALSE,
       custom.model.names = model.names.multi.2,
       custom.coef.names = coef.names.multi,
       include.pvalues=TRUE,
       caption="Logistic multilevel random intercept model for social and individual blame type of explanation")

### 2013-11-09 finalPlots.Rmd
hieman epätoivoinen commit enne mikon tekstin lisäämistä
Tein takautuvasti vielä muutokset artikkelin taulukkokoodeihin ja poistin jotain mitä olin jo poistanut. (siis olisi pitänyt committaa uusimmat muutokset ennen mikko branchin yhdistämistä)

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=TRUE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=10)
```

```{rattribFinalPlotsLoad}
library(ggplot2)
library(gridExtra)
library(plyr)
library(grid)
#########################################
#########################################
setwd("~/workspace/lits/attrib/attrib_year2013")
#########################################
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
#########################################
load("~/workspace/lits/attrib/attrib_year2013/data/lits.RData")
```

@@

t3 <- subset(macro, group_fine != 'West Europe')
west <- subset(macro, group_fine == 'West Europe')
#t3 <- macro
#########################################
t3$group1 <- "group1"
func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, gdpchange07.10) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=gdpchange07.10, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(data=cnames, aes(gdpchange07.10,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpchange07.10, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpchange07.10, 
                          y=socialBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=gdpchange07.10, 
                           y=socialBlame, label=cntry),
            alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for social blame type of explanation (%)") + 
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, gdpchange07.10) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=gdpchange07.10, 
                        y=individualBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5, color="black") +
  geom_text(data=cnames, aes(gdpchange07.10,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpchange07.10, 
             y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpchange07.10, 
                            y=individualBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=gdpchange07.10, 
                           y=individualBlame, label=cntry),
            alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for individual blame type of explanation (%)") +
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

@@

func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$uw_gini)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, uw_gini) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=uw_gini, y=socialBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(uw_gini,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Gini coefficient", 
       y = "Support for social blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=uw_gini, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=uw_gini, 
                            y=socialBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=uw_gini, 
                           y=socialBlame, label=cntry),
            alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(20,60)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$uw_gini)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, uw_gini) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=uw_gini, y=individualBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(uw_gini,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Gini coefficient", 
       y = "Support for individual blame type of explanation (%)") +
  geom_point(size=1.5) +  
  geom_point(data=t4, aes(x=uw_gini, 
                          y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=uw_gini, 
                            y=individualBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=uw_gini, 
                           y=individualBlame, label=cntry),
            alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(20,60)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

@@

func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$wbgi_vae)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, wbgi_vae) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=wbgi_vae, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(wbgi_vae,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Voice and Accountability Index 2011", 
       y = "Support for social blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=wbgi_vae, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=wbgi_vae, 
                            y=socialBlame,
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=wbgi_vae, 
                           y=socialBlame, label=cntry),
            alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$wbgi_vae)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, wbgi_vae) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=wbgi_vae, 
                        y=individualBlame, label=cntry)) +
geom_smooth(method=lm, se=FALSE, color="Dim Grey", linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(wbgi_vae,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x ="Voice and Accountability Index 2011", 
       y = "Support for individual blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=wbgi_vae, 
                          y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=wbgi_vae, 
                            y=individualBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=wbgi_vae, 
                           y=individualBlame, label=cntry),
            alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

@@

>>>>

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=FALSE,eval=TRUE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=10)
```

```{rattribFinalPlotsLoad}
library(ggplot2)
library(gridExtra)
library(plyr)
library(grid)
#########################################
#########################################
setwd("~/workspace/lits/attrib/attrib_year2013")
#########################################
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2","#D55E00", "#CC79A7")

#########################################
load("~/workspace/lits/attrib/attrib_year2013/data/lits.RData")
```

@@

t3 <- subset(macro, group_fine != 'West Europe')
west <- subset(macro, group_fine == 'West Europe')
#t3 <- macro
#########################################
t3$group1 <- "group1"
func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, gdpchange07.10) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=gdpchange07.10, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +  
  geom_text(data=cnames, aes(gdpchange07.10,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpchange07.10, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpchange07.10, 
                          y=socialBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=gdpchange07.10, 
                           y=socialBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for social blame type of explanation (%)") + 
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, gdpchange07.10) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=gdpchange07.10, 
                        y=individualBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5, color="black") +
  geom_text(data=cnames, aes(gdpchange07.10,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpchange07.10, 
             y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpchange07.10, 
                            y=individualBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=gdpchange07.10, 
                           y=individualBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for individual blame type of explanation (%)") +
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

@@

func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$uw_gini)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, uw_gini) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=uw_gini, y=socialBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(uw_gini,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Gini coefficient", 
       y = "Support for social blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=uw_gini, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=uw_gini, 
                            y=socialBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=uw_gini, 
                           y=socialBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(20,60)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$uw_gini)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, uw_gini) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=uw_gini, y=individualBlame, label=cntry)) +
  geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +  
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(uw_gini,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Gini coefficient", 
       y = "Support for individual blame type of explanation (%)") +
  geom_point(size=1.5) +  
  geom_point(data=t4, aes(x=uw_gini, 
                          y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=uw_gini, 
                            y=individualBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=uw_gini, 
                           y=individualBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(20,60)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

@@

func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$wbgi_vae)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, wbgi_vae) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=wbgi_vae, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(wbgi_vae,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Voice and Accountability Index 2011", 
       y = "Support for social blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=wbgi_vae, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=wbgi_vae, 
                            y=socialBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=wbgi_vae, 
                           y=socialBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$wbgi_vae)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, wbgi_vae) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=wbgi_vae, 
                        y=individualBlame, label=cntry)) +
geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(wbgi_vae,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x ="Voice and Accountability Index 2011", 
       y = "Support for individual blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=wbgi_vae, 
                          y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=wbgi_vae, 
                            y=individualBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=wbgi_vae, 
                           y=individualBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

@@

```{rattribFinalPlotsMap}
library(RColorBrewer)
library(mapproj)
library(maptools)
library(rgdal)
map <- suppressWarnings(readOGR(dsn="/home/aurelius/workspace/data/shapefiles/lits/", 
                                layer="lits_all_simple"))

map$NAME <- as.character(map$NAME)
map$NAME[map$NAME == "United Kingdom"] <- 'Great Britain'
map$group_analysis[map$NAME %in% c('France','Germany',
                                        'Great Britain',
                                        'Italy','Sweden')] <- 'Western Europe'

map$group_analysis[map$NAME %in% c('Czech Republic','Estonia',
                                        'Hungary','Bulgaria',
                                        'Latvia','Lithuania',
                                        'Poland','Slovakia',
                                        'Slovenia','Romania')] <- 'CEE'

map$group_analysis[map$NAME %in% c('Armenia','Azerbaijan',
                                        'Belarus','Georgia',
                                        'Kazakhstan','Kyrgyzstan',
                                        'Moldova','Tajikistan',
                                        'Ukraine','Uzbekistan','Russia')] <- 'CIS'
map$NAME <- as.factor(map$NAME)

map$group_analysis <- factor(map$group_analysis, levels=c("Western Europe",
                                                             "CEE",
                                                             "CIS",
                                                             NA))

# shapefile into data.frame
map@data$id <- rownames(map@data)
library(ggplot2)
map.points <- fortify(map, region="id")
map.df <- merge(map.points, map@data, by="id")
# only east of longitude -25
map.df <- subset(map.df, long >= -15 & long <= 80)
# names for countries in analysis (excluding others)
namedata <- map.df[!is.na(map.df$group_analysis),]
cnames <- stats:::aggregate.formula(cbind(long, lat) ~ NAME, data=namedata, mean)

mapplot <- ggplot(map.df, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = group_analysis)) + # or group_fine !!
  scale_fill_manual(values=cbPalette) +
  geom_polygon(data = map.df, aes(long,lat), fill=NA, color = "white", size=.3) +
  geom_text(data=cnames, aes(long, lat, label = NAME, group=NAME), size=2, color="black") +
  coord_map(project="orthographic") +
  theme_minimal() + 
  theme(legend.position="top") +
  theme(legend.title=element_blank()) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank()) +
  theme(axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank()) +
  theme(legend.key.size = unit(3, "mm"))

pdf("figure/mapplot.pdf", width=14/2.54, height=10/2.54)
mapplot
dev.off()

ppi <- 300
png("figure/mapplot.png", width=14/2.54*ppi, height=10/2.54*ppi, res=ppi)
mapplot
dev.off()

![](figure/mapplot.png)
